---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# albersextra

<!-- badges: start -->
<!-- badges: end -->

The goal of albersextra is to include Puerto Rico, the Virgin Islands and Guam in the traditional Albers maps. Also, albersextra will make it easier to map line, point and other data in the Albers projection.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hlendway/albersextra")
```
## Examples

Sample datasets include information from the National Inventory of Dams and the National Bridge Inventory. 

```{r example}
library(albersextra)
## Pull in sample data for mapping
head(bridges) ## Data slice from National Bridge Inventory
```

The standard Albers conic projection isn't great for points in Alaska, Hawaii, Puerto Rico, Guam and the U.S. Virgin Islands. (AK and HI are taken care of with AlbersUSA.
)
```{r example2, fig.height = 3, fig.width = 10}
# Map the dams sample data.
library(ggplot2)
ggplot() + geom_sf(data = dams) + coord_sf()
```

```{r example3, fig.height = 5.2, fig.width = 10}
# Map the bridges sample data.
library(ggplot2)
ggplot() + geom_sf(data = bridges) + coord_sf()
```

To convert your own set of point data with a latitude and longitude to an sf object, try the following: 

```{r example4, eval=FALSE, include=TRUE}
# To convert your own point data for use with albersextra
bridges <- read_sf("data-raw/bridges.csv", ## Replace with your own csv file
                   options = c("X_POSSIBLE_NAMES=longitude",
                               "Y_POSSIBLE_NAMES=latitude"))
```
