---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# albersextra

<!-- badges: start -->
<!-- badges: end -->

The goal of albersextra is to include Puerto Rico, the Virgin Islands and Guam in the traditional Albers maps. Also, albersextra will make it easier to map line, point and other data in the Albers projection.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hlendway/albersextra")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(albersextra)
## Pull in sample data for mapping
head(bridges) ## Data slice from National Bridge Inventory
```

```{r example2}
# Map the dams sample data.
library(ggplot2)
ggplot() + geom_sf(data = dams) + coord_sf()
```

```{r example3}
# Map the bridges sample data.
library(ggplot2)
ggplot() + geom_sf(data = bridges) + coord_sf()
```
